Audio Interface of an Active Perception Navigation Aid for People with Visual Impairments

### 2019-07-08 paper.tex
Added pan description

\begin{figure}
  \centering
  %\subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_headphone.png}}
  \includegraphics[width=0.5\columnwidth]{figures/tango_headphone.png}}
  %~
  %\subfloat[]{\label{fig:participant}\includegraphics[width=0.35\columnwidth]{figures/vi_participant.pdf}}
  \caption{Pictures of the Tango device and bone-conducting headphones the system is based on (left) and both in use in an experiment (right).}\label{fig:tango-headphone}
\end{figure}

A similar approach was used in \todo{ref previous varying pitch study}, but the study did not focus on the interface's efficacy.
Indeed, this work serves as an initial study into such an interface.
The contribution of this work is an effective approach to addressing the shortcomings of bone-conducting headphones in transmitting spatialised sounds through a generic sound library, as well as initial experiments demonstrating its effectiveness.

@@

Humans localise a sound source in 3 dimensions by considering cues recorded in one ear (monaural cues) and comparing cues derived at both ears (binaural cues).
The binaural cues include time differences of arrival and intensity differences that help to determine a source's location on the horizontal plane.
Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
The user's anatomy acts as a filter and the direction the sound wave hits the body activates different filter resonances, attenuating or accentuating different frequency bands.
When the modified sound enters the inner ear, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the vertical plane. 
The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one does.

@@

The guidance target is presented to the user in terms of pan and elevation angles, indicating the angle adjustments that are required to point the device camera at the target location.
Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution.
However, the audio guidance signals are delivered to the user with a set of bone-conducting headphones that bypass the user's outer-ear structure and since this structure plays an important role in localising a sound source's elevation, an alternative mode of conveying the elevation angle is required.
For this work, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle.

@@

Binaural comparison cues are used to

>>>>

\begin{figure}
  \centering
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.4\columnwidth]{figures/tango_headphone.png}}
  %\includegraphics[width=0.5\columnwidth]{figures/tango_headphone.png}}
  ~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.25\columnwidth]{figures/vi_participant.pdf}}
  \caption{Pictures of the Tango device and bone-conducting headphones the system is based on (left) and both in use in an experiment (right).}\label{fig:tango-headphone}
\end{figure}

A similar approach was used in\cite{durette2008visuo}, but the study did not focus on or investigate the interface's efficacy.
Indeed, this work serves as an initial study into an interface that can effectively communicate the pan and elevation angles of a target location through a set of bone-conducting headphones using a standard head-related transfer function (HRTF).
Furthermore, we demonstrate our approach's effectiveness through a simple experiment.
%The contribution of this work is an effective approach to addressing the shortcomings of playing spatialised sound through bone-conducting headphones, as well as initial experiments demonstrating its effectivenesst
%Furthermore, we demonstrate that such an interface is effective at communicating

@@

Humans localise a sound source in 3 dimensions by considering cues recorded in one ear (monaural cues) and comparing cues derived at both ears (binaural cues)\cite{blauert1997spatial,blauert1969sound}.
The binaural cues include time differences of arrival and intensity differences that help to determine a source's location on the horizontal plane.
Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
The user's anatomy acts as a filter and the direction the sound wave hits the body activates different filter resonances, attenuating or accentuating different frequency bands.
When the modified sound enters the inner ear, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the vertical plane. 
The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one does.

@@

The guidance target is presented to the user in terms of pan and elevation angles, indicating the angle adjustments that are required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution\cite{klatzky2006cognitive}.
However, the audio guidance signals are delivered to the user with a set of bone-conducting headphones that bypass the user's outer-ear structure and since this structure plays an important role in localising a sound source's elevation\cite{blauert1969sound}, an alternative mode of conveying the elevation angle is required.
For this work, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
The pan angle can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conducting headphones\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.\todo{cite bone cnducting work}

\begin{figure}
  \centering
  \includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}
  \caption{A diagram showing the device's frame of reference and the target's pan and tilt angles.}\label{fig:cam-coords}
\end{figure}

%The audio signal used for this work is a simple \SI{10}{\hertz} sinusoidal wave that is easy to manipulate and analyse.
%People have trouble localising a pure sine wave given its lack of spectral features

@@

The human audition system uses binaural comparison cues, such as the inter-aural time and level differences (ITD and ILD respectively), to localise a sound source on the horizontal plane.
The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
For example, a sound that comes from the individual's right, will hit the right ear first with a slightly higher volume.

In this work, a pure sinusoidal wave oscillating at \SI{10}{\hertz} was used. 
People typically have trouble localising a pure tone devoid of a rich spectral signature.
However, the ITD and ILD is independent of the tone's spectral make-up and the elevation angle is given through a different mechanism.
A pure sine wave is therefore sufficient to convey the target's pan angle.
To transform the signal, we used OpenAL's default HRTF, based on the MIT's KEMAR dataset\cite{hiebert2005openal,gardner1995hrtf}, that uses the user and targets' positions as input and outputs a transformed audio signal.
